Data analysis

### 2025-03-04 processing/01-proc-data.qmd
Up data prep and analysis V1

---
title: "Data preparation"
subtitle: "Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)"
author: "Andreas Laffert, Research asistant"
date: today
lang: en
fontsize: 12pt
format:
  html:
    toc: true
    toc-location: right
    toc-depth: 2
    toc-expand: 2
    toc-title: Contents
    number-sections: true
    number-depth: 3
    theme:
      - cosmo
      - edumer_html.scss
    code-link: true
    title-block-banner: true
  pdf:
    number-sections: true
    number-depth: 3
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Data preparation"
subtitle: "Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)"
author: "Researcher"
date: today
lang: en
fontsize: 12pt
format:
  html:
    toc: true
    toc-location: right
    toc-depth: 2
    toc-expand: 2
    toc-title: Contents
    number-sections: true
    number-depth: 3
    theme:
      - cosmo
      - edumer_html.scss
    code-link: true
    title-block-banner: true
  pdf:
    number-sections: true
    number-depth: 3
editor_options: 
  chunk_output_type: console
---

### 2025-03-04 processing/02-analysis.qmd
Up data prep and analysis V1

---
title: "Data analysis"
subtitle: "Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)"
author: "Andreas Laffert, Research asistant"
date: today
lang: en
fontsize: 12pt
format:
  html:
    code-fold: true
    code-summary: "Show the code"
    toc: true
    toc-location: right
    toc-depth: 2
    toc-expand: 2
    toc-title: Contents
    number-sections: true
    number-depth: 3
    theme:
      - cosmo
      - edumer_html.scss
    code-link: true
    title-block-banner: true
  pdf:
    number-sections: true
    number-depth: 3
editor_options: 
  chunk_output_type: console
---

@@

texreg::htmlreg(list(m1, m2, m3, m4, m5, m6, m7),
               custom.model.names = c(paste0("Model ", seq(1:7))),
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               digits = 3,
               groups = list("Age (Ref. = 18-29)" = 10:12,"Political identification (Ref.= Left)" = 15:17, "Wave (Ref.= 2016)" = 19:23),
               custom.note = "\\item Note: Cells contain regression coefficients with standard errors in parentheses. %stars. \\\\ \\item Source: own elaboration with pooled data from ELSOC 2016-2023 (n = 16219).",
               threeparttable = T,
               leading.zero = T,
               float.pos = "h!",
               use.packages = F,
               booktabs = T,
               scalebox = 1)
```

>>>>

---
title: "Data analysis"
subtitle: "Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)"
author: "Researcher"
date: today
lang: en
fontsize: 12pt
format:
  html:
    code-fold: true
    code-summary: "Show the code"
    toc: true
    toc-location: right
    toc-depth: 2
    toc-expand: 2
    toc-title: Contents
    number-sections: true
    number-depth: 3
    theme:
      - cosmo
      - edumer_html.scss
    code-link: true
    title-block-banner: true
  pdf:
    number-sections: true
    number-depth: 3
editor_options: 
  chunk_output_type: console
---

@@

texreg::htmlreg(list(m1, m2, m3, m4, m5, m6, m7),
               custom.model.names = c(paste0("Model ", seq(1:7))),
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               digits = 3,
               groups = list("Age (Ref. = 18-29)" = 10:12,"Political identification (Ref.= Left)" = 15:17, "Wave (Ref.= 2016)" = 19:23),
               custom.note = "\\item Note: Cells contain regression coefficients with standard errors in parentheses. %stars. \\\\ \\item Source: own elaboration with pooled data from ELSOC 2016-2023 (n = 4364).",
               threeparttable = T,
               leading.zero = T,
               float.pos = "h!",
               use.packages = F,
               booktabs = T,
               scalebox = 1)
```
